6.867 Problem Set 2

### 2015-10-26 HW2/tex/HW2.tex
[hw2] getting up to date.

\begin{table}
\captionof{table}{Performance of Linear SVM on provided data sets}
\begin{tabular}{llllll}
\toprule
{} & dataset & classification error rate (training set) & classification error rate (validation set) \\
\midrule
  & data\_stdev1 & 0.00\% & 0.00\% \\
  & data\_stdev2 & 9.50\% & 7.50\% \\
  & data\_stdev4 & 26.00\% & 23.50\% \\
  & data\_nonsep & 49.50\% & 51.25\% \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\captionof{table}{Performance of Linear SVM on provided data sets}
\begin{tabular}{c c|c|c|c|c|c}
\toprule
{} & dataset & $w_0$ & $w_1$ & $w_2$ & classification error rate (training) & classification error rate (validation) \\
\midrule
  & data\_stdev1 & 0.31 & 5.42 & 0.87 & 0.00\% & 0.00\% \\
  & data\_stdev2 & 9.09e-2 & 9.83e1 & 9.11e1 & 9.50\% & 7.50\% \\
  & data\_stdev4 & -2.05e-2 & 2.58e2 & 2.40e2 & 26.00\% & 23.50\% \\
  & data\_nonsep & 2.56e-3 & 4.23e2 & 3.84e2 & 49.50\% & 51.25\% \\
\bottomrule
\end{tabular}
\end{table}
